---
title: "Using CarbPack for Hardware Detection and Performance Tracking"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using CarbPack for Hardware Detection and Performance Tracking}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The `CarbPack` package provides tools for hardware detection and performance tracking in R. This vignette demonstrates how to use the main functions of the package to detect hardware specifications, start a performance tracker, and save the tracking results.

## Prerequisites

Before proceeding, ensure that the `CarbPack` package is installed and loaded.

```{r}
# Install the package if you haven't already
# install.packages("CarbPack")

# Load the package
library(CarbPack)
```

## Step 1: Detect Hardware

The first step is to detect the hardware specifications of your machine. This can be useful for understanding the computational environment where your analysis is performed.

```{r}
# Detect hardware specifications
hardware_info <- CarbPack::detect_hardware()
```

The `detect_hardware()` function returns information about your machine, such as the CPU model, number of cores, and available memory.

## Step 2: Start the Performance Tracker

After detecting the hardware, start the performance tracker. This function records the time at which tracking begins, which will later be used to measure the duration of the process.

```{r}
# Start the performance tracker
start_time <- CarbPack::tracker_start()
```

The `tracker_start()` function marks the beginning of the tracking period.

## Step 3: Main Code Execution

Insert your main code here, which is the computational work or analysis you want to track. For example, you might run a simulation, perform data processing, or execute a machine learning algorithm.

```{r}
# Insert main code here
# Example:
# result <- some_computation_function(data)
```

## Step 4: Stop the Tracker and Save Results

Once the main code execution is complete, stop the tracker and save the results. This function will calculate the elapsed time and optionally save the hardware and performance information to a file.

```{r}
# Stop the performance tracker and save results
CarbPack::tracker_stop(
  hardware = hardware_info,
  start_time = start_time
)
```

The `tracker_stop()` function takes the hardware information and start time as arguments, calculates and print the duration of the process.

## Conclusion

The `CarbPack` package provides an easy way to monitor hardware and track the performance of your R scripts. By following the steps outlined in this vignette, you can collect useful information about your computational environment and the execution time of your code.

For more details on the package functions, refer to the package documentation.
